### 2023-02-09 documentation/paper.tex
Finish

\begin{figure}
      \hspace{\fill}
      \includegraphics[width=0.9\linewidth]{images/noise.png}
      \hspace{\fill}
      \centering
      \caption{
            Left images: Noisy low light sample from bursts provided by the supplemental dataset
            to \cite{Hasinoff2016burst}. Top row shows full image while bottom shows zoom in noisy
            area.
            Right images: Processed burst images with settings gain $g=1.0$ and dynamic 
            range compression $c=2.5$.
      }
      \label{fig:noise}
\end{figure}

@@

@@

While small movements could be processed well, it should be investigated how to 
process fast moving objects over a long distance. For this purpose, an image burst 
of a road with moving cars at night was recorded, which is shown in \cref{fig:moving}. 
Although the low light situation was basically processed satisfactorily and not 
too fast cars could be aligned well, clear ghosting artifacts can be seen in the 
for the very fast moving white car.

@@

>>>>

@@

\begin{figure}
      \hspace{\fill}
      \includegraphics[width=0.8\linewidth]{images/noise.png}
      \hspace{\fill}
      \centering
      \caption{
            Left images: Noisy low light sample from bursts provided by the supplemental dataset
            to \cite{Hasinoff2016burst}. Top row shows full image while bottom shows zoom in noisy
            area.
            Right images: Processed burst images with settings gain $g=1.0$ and dynamic 
            range compression $c=2.5$.
      }
      \label{fig:noise}
\end{figure}

@@

While small movements could be processed well, it should be investigated how to 
process fast moving objects over a long distance. For this purpose, an image burst 
of a road with moving cars at night was recorded, which is shown in \Cref{fig:moving}. 
Although the low light situation was basically processed satisfactorily and not 
too fast cars could be aligned well, clear ghosting artifacts can be seen in the 
for the very fast moving white car.

@@

In a next step, the results could be compared with those of a more up-to-date burst processing 
pipeline in terms of image quality and performance. A suitable candidate would be the neural 
network-based approach presented by Dudhane et al. (2022) \cite{Dudhane2022restoration}, 
as the individual steps of this pipeline are fundamentally different from those of the 
HDR+ pipeline and the authors make their source code available in an open source project
\cite{Dudhane2022git}.
